The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes

### 2022-09-09 report/accepted-manuscript.Rmd
final version

---
output: 
  stevetemplates::article:
    fig_caption: true
bibliography: references.bib
urlcolor: black
linkcolor: black
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage[para,online,flushleft]{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{hyperref}
   - \usepackage{array}   
   - \usepackage{caption}
   - \usepackage{graphicx}
   - \usepackage{epstopdf}
   - \usepackage{siunitx}
   - \usepackage{multirow}
   - \usepackage{hhline}
   - \usepackage{calc}
   - \usepackage{tabularx}
   - \usepackage{fontawesome}
   - \usepackage{amsthm}
   - \newtheorem{hypo}{Hypothesis}
biblio-style: apsr
title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
author:
  - name: Maurits Meijers
  - affiliation: Radboud University Nijmegen
  - name: Mariken A.C.G. van der Velden
  - affiliation: Vrije Universiteit Amsterdam
thanks: "Replication files are available on the author's Github account (https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md). **Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
anonymous: FALSE
abstract: "Populists believe in the sovereignty of the people. Yet, the people can be construed in ethnic terms or in civic terms. Using a novel wording experiment in Germany (N=7,034), we examine whether ethnic or civic conceptions of 'the people' affect respondents' adherence agreement to key populist attitude items. '_Volk_' in German has an ethno-nationalist connotation and has been used throughout history to signify 'ethnic Germans'. The concept '_Bürger_', or citizens, by contrast, lacks an ethnic undercurrent. Similar ethnic connotations of 'the people' are also common in other languages. We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item. This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right. Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes. When populist attitudes are measured with an ethnic understanding of the 'the people', the construct is biased toward right-wing populism, inhibiting the measurement of populism as a `thin-ideology'. Moreover, we demonstrate the importance of careful translations in comparative research, since some translated synonyms carry different meanings, and thereby change the concept under investigation."

@@

[^1]: A scale is measurement invariant across groups if subjects with identical levels of the latent construct have the same expected raw-score on the measure [@drasgow1985equivalence].
[^2]: All analytical material for replication can be found in our online Research Compendium: https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md (anonymized for the review process).

@@

[^3]: A power analysis is conducted and reported on our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).

@@

```
```{r results-h1,out.width = "85%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Differences in Ethnic and Civic Conceptions of the People"}
knitr::include_graphics(here("report/figures", "h1-1.png"))
```
To examine whether civic conceptions of the people elicit different responses than ethnic concepts, we experimentally vary the wording of two of the six items in the scale proposed by @akkerman2014, see Table \ref{tab:popatt}. 
In the original Akkerman et al. scale deployed in the Netherlands, the items `POP1` and `POP2` were phrased in ethnic terms (i,e., with reference to _het volk_). 
We randomize whether respondents received a ethnic framing (i.e., with reference to 'the people; or _das Volk_) or a civic framing (i.e., with reference to 'citizens', or _Bürger_). 
A balance test, reported in our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md), demonstrates that the allocation of the treatment was fully random.
The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
All the other items were kept constant.[^4].

@@

[^5]: Our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md) demonstrates that there are no other socio-demographic variables that mediate the effect.

@@

In addition, we have explored how the effect of an ethnic conception of the people vis-à-vis a civic conception vary across age and region. People that are born during or closely after WWII  as well as people born and/or living in certain regions in Germany (e.g. the East or Bavaria) could potentially have a different reaction to the two conceptions of the people -- all figures can be found in the Online Appendix (Figure A-2, p. A9) as well as in our Online Research Compendium.
**_Age_.** We demonstrate in the upper-left panel of Figure A-2 in the OA that for younger age groups (i.e. all age groups younger than 50 years old) there is no difference for the civic and ethnic conception of the people. Yet, for the older population (50 years old and more) we see that people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment for both `POP1` (''The politicians need to follow the will of the people''), the effect size is about half a point (i.e. half a standard deviation) and `POP2` (''the people, not politicians, should make the most important political decisions''). The effect size is still small in substantive terms: between a `0.1` and `0.3` increase on a 5-point scale.
**_Region_.** We show in the upper-right panel of Figure A-2 in the OA that while for most regions in Germany, there is no statistically significant difference between receiving an ethnic or a civic treatment. Yet, for the regions Sleswig-Holstein (i.e. the region bordering Denmark) and Hessen (mid-Germany), we see that people receiving the ethnic treatment report lower levels of agreement with the items compared to people receiving the civic treatment for both `POP1` and `POP2`. The same effect holds for the region Bremen for `POP1` and for Berlin and North-Rhine Westphalia for `POP2`. This indicates that in Western districts, people are sensitive to the ethnic conception of the 'people' and all else equal, under-report their populist attitudes by approximately `0.5` points on a 5-point scale.

>>>>

---
output: 
  stevetemplates::article:
    fig_caption: true
bibliography: references.bib
urlcolor: black
linkcolor: black
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage[para,online,flushleft]{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{hyperref}
   - \usepackage{array}   
   - \usepackage{caption}
   - \usepackage{graphicx}
   - \usepackage{epstopdf}
   - \usepackage{siunitx}
   - \usepackage{multirow}
   - \usepackage{hhline}
   - \usepackage{calc}
   - \usepackage{tabularx}
   - \usepackage{fontawesome}
   - \usepackage{amsthm}
   - \newtheorem{hypo}{Hypothesis}
biblio-style: apsr
title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
author:
  - name: Maurits Meijers
  - affiliation: Radboud University Nijmegen
  - name: Mariken A.C.G. van der Velden
  - affiliation: Vrije Universiteit Amsterdam
thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes). **Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
anonymous: FALSE
abstract: "Populists believe in the sovereignty of the people. Yet, the people can be construed in ethnic terms or in civic terms. Using a novel wording experiment in Germany (N=7,034), we examine whether ethnic or civic conceptions of 'the people' affect respondents' adherence agreement to key populist attitude items. '_Volk_' in German has an ethno-nationalist connotation and has been used throughout history to signify 'ethnic Germans'. The concept '_Bürger_', or citizens, by contrast, lacks an ethnic undercurrent. Similar ethnic connotations of 'the people' are also common in other languages. We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item. This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right. Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes. When populist attitudes are measured with an ethnic understanding of the 'the people', the construct is biased toward right-wing populism, inhibiting the measurement of populism as a `thin-ideology'. Moreover, we demonstrate the importance of careful translations in comparative research, since some translated synonyms carry different meanings, and thereby change the concept under investigation."

@@

[^1]: A scale is measurement invariant across groups if subjects with identical levels of the latent construct have the same expected raw-score on the measure [@drasgow1985equivalence].
[^2]: All analytical material for replication can be found in our online Research Compendium: https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes.

@@

[^3]: A power analysis is conducted and reported on our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).

@@

```
```{r results-h1,out.width = "85%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Differences in Ethnic and Civic Conceptions of the People"}
knitr::include_graphics(here("report/figures", "h1-1.png"))
```
To examine whether civic conceptions of the people elicit different responses than ethnic concepts, we experimentally vary the wording of two of the six items in the scale proposed by @akkerman2014, see Table \ref{tab:popatt}. 
In the original Akkerman et al. scale deployed in the Netherlands, the items `POP1` and `POP2` were phrased in ethnic terms (i,e., with reference to _het volk_). 
We randomize whether respondents received a ethnic framing (i.e., with reference to 'the people; or _das Volk_) or a civic framing (i.e., with reference to 'citizens', or _Bürger_). 
A balance test, reported in our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes), demonstrates that the allocation of the treatment was fully random.
The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
All the other items were kept constant.[^4].

@@

[^5]: Our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes) demonstrates that there are no other socio-demographic variables that mediate the effect.

@@

In addition, we have explored how the effect of an ethnic conception of the people vis-à-vis a civic conception vary across age and region. People that are born during or closely after WWII  as well as people born and/or living in certain regions in Germany (e.g. the East or Bavaria) could potentially have a different reaction to the two conceptions of the people -- all figures can be found in the Online Appendix (Figure A-2, p. A9) as well as in our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
**_Age_.** We demonstrate in the upper-left panel of Figure A-2 in the OA that for younger age groups (i.e. all age groups younger than 50 years old) there is no difference for the civic and ethnic conception of the people. Yet, for the older population (50 years old and more) we see that people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment for both `POP1` (''The politicians need to follow the will of the people''), the effect size is about half a point (i.e. half a standard deviation) and `POP2` (''the people, not politicians, should make the most important political decisions''). The effect size is still small in substantive terms: between a `0.1` and `0.3` increase on a 5-point scale.
**_Region_.** We show in the upper-right panel of Figure A-2 in the OA that while for most regions in Germany, there is no statistically significant difference between receiving an ethnic or a civic treatment. Yet, for the regions Sleswig-Holstein (i.e. the region bordering Denmark) and Hessen (mid-Germany), we see that people receiving the ethnic treatment report lower levels of agreement with the items compared to people receiving the civic treatment for both `POP1` and `POP2`. The same effect holds for the region Bremen for `POP1` and for Berlin and North-Rhine Westphalia for `POP2`. This indicates that in Western districts, people are sensitive to the ethnic conception of the 'people' and all else equal, under-report their populist attitudes by approximately `0.5` points on a 5-point scale.
